### 2016-01-18 paper.tex
Add Vince's recommended edits plus more to the abstract

The mechanical power, total rotor drag, and near-wake flow of a 1:6 scale
Reference Model 2 (RM2) vertical-axis cross-flow turbine were measured
experimentally in a towing tank. Performance was measured at multiple Reynolds
numbers by varying tow carriage speed, and weak linear $Re$-dependence was
achieved at a turbine diameter Reynolds number $Re_D \approx 10^6$. An optimal
tip speed ratio $\lambda_0 = 3.1$ was chosen, at which the near wake velocity
was measured at 1 m $(x/D=0.93)$ downstream. Mean velocity, turbulence, and mean
kinetic energy transport mechanisms were compared and contrasted with results
from a high solidity turbine acquired with the same test apparatus. Overall,
lower levels of streamwise wake recovery were calculated for the RM2 rotor---a
consequence of both the relatively low solidity and tapered blades. The effects
of blade support strut drag on turbine performance were investigated by covering
the rotor's NACA 0021 struts with cylinders. As expected, this modification
drastically reduced rotor power coefficient. Strut drag was also measured for
the NACA 0021 and cylindrical configurations with the blades removed. These
measurements provide a comprehensive open dataset for validating numerical
models' predictive capabilities for low solidity rotors.

>>>>

The mechanical power, total rotor drag, and near-wake flow of a 1:6 scale
physical reference model vertical-axis cross-flow turbine were measured
experimentally in a towing tank, to provide a comprehensive open dataset for
validating numerical models. Performance was measured at multiple Reynolds
numbers by varying tow carriage speed. Weak linear $Re$-dependence was achieved
at a turbine diameter Reynolds number $Re_D \approx 10^6$. An optimal tip speed
ratio $\lambda_0 = 3.1$ was chosen, at which the near wake velocity was measured
at 1 m $(x/D=0.93)$ downstream. Mean velocity, turbulence kinetic energy, and
mean kinetic energy transport were compared with results from a high solidity
turbine acquired with the same test apparatus. Overall, lower levels of
streamwise wake recovery were calculated for the RM2 case---a consequence of
both the relatively low solidity and tapered blades reducing blade tip vortex
shedding---responsible for mean vertical advection---and lower levels of
turbulence caused by higher operating tip speed ratio and therefore reduced
dynamic stall. The effects of blade support strut drag on turbine performance
were investigated by covering the rotor's NACA 0021 struts with cylinders. As
expected, this modification drastically reduced the rotor power coefficient.
Strut drag was also measured for the NACA 0021 and cylindrical configurations
with the blades removed.
